Cosmic Web

### 2014-01-31 paper/main.tex
FA paragraph

@@

The algorithm to compute the potential is grid based. First we
interpolate the potential into a cubic grid and smooth it with a
gaussian kernel. Then we obtain the gravitational potential and use
finite differences to compute the Hessian at every point in the
grid. Physically speaking, the cosmic web features are scale
dependent and the grid size has to be chosen with respect to the
physical scales of the problem at hand.

@@

@@

\citep{Hillier98}

\begin{table}
\begin{center}
\begin{tabular}{lcccc}\hline\hline
Sample & Peak & Filament & Sheet & Void\\
       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
2$\sigma$ & 10 (8.1) & 59 (48.3) & 48 (39.3) & 5 (4.0)\\  
3$\sigma$ & 4 (8.5) & 24 (51.0) &  18 (38.2) & 1 (2.1)\\
General & 1307 (23.8) & 1470 (26.8) & 1769 (32.3) & 927 (16.9)\\\hline
\end{tabular}
\caption{
Number of pairs in the four different kinds of environmtns. In
parethesis the same number as a percentage of the
total population. 
\label{table:models}}
\end{center}
\end{table}

>>>>

\subsection{The Bolshoi simulation}

@@

The fractional anisotropy (FA) \citep{Libeskind2013} is a quantity
that measures the relative strength of the three eigenvalues and
therefore can be interpreted as the relative strenght of
compression/tension exterted by the tidal field. It is defined as:

\begin{equation}
FA=
\end{equation}
%
an additional advantage of the FA is that it does not depend on the
choice of $\lambda_{\rm th}$ and can be used as a broad gauge of the
kinds of tidal forces on the Local Group.

The algorithm to compute the potential is grid based. First we
interpolate the density into a cubic grid and smooth it with a
gaussian kernel. Then we obtain the gravitational potential and use
finite differences to compute the Hessian at every point in the
grid. Physically speaking, the cosmic web features are scale
dependent and the grid size has to be chosen with respect to the
physical scales of the problem at hand.

@@

\section{Local Group Samples}

@@

The first results we explore is the kind of environment occupied by
our LGs. We find that LGs in the restricted $2\sigma$ and $3\sigma$
samples prefer by large to be in filaments and sheets. Almost $\sim 50\%$ of the
pairs in both cases can be found in filaments while $\sim 40\%$ can be
found in sheets. This proportion is in stark contrast to the
environments for the general pair sample. In that case only $\sim
27\%$ and $\sim 33\%$ can be found in filaments and sheets,
repectively. There is a considerable fraction of pairs that are
located in peaks ($\sim 25\%$) and voids ($\sim 15\%$). These results
and the exact numbers are presented in Table \ref{table:web_type}.

\begin{table}
\begin{center}
\begin{tabular}{lcccc}\hline\hline
Sample & Peak & Filament & Sheet & Void\\
       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
2$\sigma$ & 10 (8.1) & 59 (48.3) & 48 (39.3) & 5 (4.0)\\  
3$\sigma$ & 4 (8.5) & 24 (51.0) &  18 (38.2) & 1 (2.1)\\
General & 1307 (23.8) & 1470 (26.8) & 1769 (32.3) & 927 (16.9)\\\hline
\end{tabular}
\caption{
Number of pairs in the four different kinds of environmtns. In
parethesis the same number as a percentage of the
total population. 
\label{table:web_type}}
\end{center}
\end{table}
